\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item{
		\textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
	}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
		\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
				\textbf{#1} & \textit{\footnotesize{#4}} \\
				\textit{\footnotesize{#3}} &	\footnotesize{#2}\\
		\end{tabular*}
		\vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
		\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
				\textbf{#1} & \textit{\footnotesize{#3}} \\
				\footnotesize{\textit{#2}} & \footnotesize{#4}
		\end{tabular*}
		\vspace{-2.4mm}
}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}

%---- End of Packages and Functions ------

%-------------------------------------------
\newcommand{\phone}{(xxx)xxx-xxxx}
\newcommand{\email}{Mr-Bossman075@gmail.com}

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------
{
\begin{multicols}{2}
	\textbf{\Large Jesse Taube} \\
	{{\footnotesize \faMicrochip} Embedded Software Engineer} \\
	{{\footnotesize \faMapMarker} Newton Massachusetts} \\
	{{\footnotesize \faGraduationCap} University of Massachusetts Lowell} \\
	\vfill\null
	\RaggedLeft
	{\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone} \\
	{\href{mailto:\email}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\email}}} \\
	{\href{https://github.com/Mr-Bossman}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}}} \\
	{\href{https://www.linkedin.com/in/jesse-taube-749351229/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}} \\
	{\href{https://jachan.dev}{\raisebox{0.0\height}{\footnotesize \faGlobe}\ {My website}}}
\end{multicols}
}
\vspace{-3mm}

%-----------Technical skills-----------------
% JS/Node, HTML+CSS
% GNU tools, Automake, KiCad
% RTOSs, Baremetal and Firmware
% TCP/IP, OpenCV, LibAV
\section{\textbf{Technical Skills and Interests}}
\begin{itemize}[leftmargin=0.05in, label={}]
		\small{\item{
		 \textbf{Languages}{: C, C++, Shell, Verilog, Python} \\
		 \textbf{Tools \& Technologies}{: Git, KVM, Linux Kernel, U-Boot} \\
		 \textbf{Protocols \& Libraries}{: Networking, C\&C++ STL, I\textsuperscript{2}C, SPI, RS232}\\
		 \textbf{Hardware}{: Experienced with reading schematics, using oscilloscopes, multi-meters, and low-speed routing} \\
		 \textbf{Areas of Interest}{: Embedded Linux, IOT and IOT security} \\
		}}
\end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
	\resumeSubHeadingListStart
		\resumeSubheading
			{D3 Engineering}{Rochester, New York}
			{Intern Kernel developer on the Nvidia Jetson Team}{May 2023 - Aug 2023}
			\vspace{-2.0mm}
			\resumeItemListStart
		\item {Linux Kernel driver development in C for GMSL and FPD-link cameras.}
		\item {Writing device trees and device tree overlays.}
		\item {Reading schematics and datasheets.}
		\item {Working with oscilloscopes and multi-meters.}
		\item {Debugging hardware and software issues, such as MIPI CSI data loss.}
		\resumeItemListEnd

		\vspace{-3.0mm}

		\resumeSubheading
			{Part-time Freelancer}{Hybrid}
			{Hardware and Software developer}{Jun 2018 - Present}
			\vspace{-2.0mm}
			\resumeItemListStart
			\item {Writing Kernel drivers for custom hardware.}
			\item {Development of custom test boards.}
			\item {UL-certified SOM-based custom motor control board with HDMI.}
			\item {Programming tutor for University and high school students.}
		\resumeItemListEnd

		\vspace{-3.0mm}

		\resumeSubheading
			{Microcenter}{Cambridge, Massachusetts}
			{Customer Service Representative}{Feb 2022 - Jan 2023}
			\vspace{-2.0mm}
			\resumeItemListStart
			\item {Communication with management and customers.}
			\item {Diagnosing and helping customers with computer problems.}
		\resumeItemListEnd

		\vspace{-3.0mm}

	\resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
		\resumeProject
			{Linux Ports} %Project Name
			{Porting of IMXRT to the Linux Kernel} %Project Name, Location Name
			{} %Event Dates

			\resumeItemListStart
			\item {Writing Kernel drivers in C and Device Trees}
			\item {Debugging over JTAG with GDB}
			\item {Using agile development with co-developers}
		\resumeItemListEnd
		\vspace{-2mm}

		\resumeProject
			{KISC-V} %Project Name
			{A KISS principle RISC-V32I CPU, written in SystemVerilog} %Project Name, Location Name
			{} %Event Dates

			\resumeItemListStart
			\item {Written in SystemVerilog and debugged with GTKWave}
			\item {Microcode generation in Python}
			\item {Custom trap handler in C and Assembly to emulate CSR instructions}
			\item {Can run No-MMU Linux}
		\resumeItemListEnd
		\vspace{-2mm}

		\resumeProject
			{Personal Blog} %Project Name
			{Blog with backend in NodeJS hosted Locally} %Project Name, Location Name
			{} %Event Dates

			\resumeItemListStart
			\item {Dynamic and static pages in NodeJS using Express}
			\item {Jquery and Bootstrap for frontend}
			\item {Locally hosted on servers running cockpits KVM}
		\resumeItemListEnd
	\resumeSubHeadingListEnd
\vspace{-8.5mm}

%-----------EDUCATION-----------
\section{\textbf{Education}}
	\resumeSubHeadingListStart
		\resumeSubheading
			{University of Massachusetts Lowell}{}
			{Bachelor of Computer Engineering}{2022-26}
		\resumeSubheading
			{Newton South High School}{}
			{LigerBots - FRC team 2877}{2022}
			{Science team}{}
	\resumeSubHeadingListEnd
\vspace{-5.5mm}
\end{document}
